### 2020-04-06 system-model.tex
:pencil2: Energy harvester

		\begin{subsubsection} {Unmodulated Power Waveform}
			As suggested in \cite{Clerckx2018b,Clerckx2016a}, we use deterministic multisine waveform to boost the harvested energy. It has no randomness over time and the equivalent input power symbol $\tilde{x}_{P,n}$ is a constant on subband $n$ (i.e. $\tilde{x}_{P,n} = 1$). Therefore, on the $n$-th subcarrier of the $m$-th transmit antenna, the power weight $w_{P,n,m} = s_{P,n,m} e^{j\phi_{P,n,m}}$ represents the complex-valued sinewave (i.e. $x_{P,n,m}(t) = w_{P,n,m}$) in the baseband. The transmit power waveform on the antenna $m$ at time $t$ is given by
			\begin{equation}	\label{eq:x{P,m}(t)}
				\begin{split}
					x_{P,m}(t)
					&= \sum_{n=1}^{N} s_{P,n,m}(t) \cos \left( 2 \pi f_n t + \phi_{P,n,m}(t) \right)	\\
					&= \Re \left\{ \sum_{n=1}^{N} x_{P,n,m}(t) e^{j2 \pi f_n t} \right\}	\\
					&= \Re \left\{ \sum_{n=1}^{N} w_{P,n,m} e^{j2 \pi f_n t} \right\}
				\end{split}
			\end{equation}
			The corresponding power waveform vector is stacked across $M$ transmit antennas as
			\begin{equation}	\label{eq:x_P(t)}
				\boldsymbol{x}_P(t) = \Re \left\{ \sum_{n=1}^{N} \boldsymbol{w}_{P,n} e^{j2{\pi}{f_n}t} \right\}
			\end{equation}
			where $\boldsymbol{w}_{P,n}=[w_{P,n,1},\dots,w_{P,n,M}]^T \in \mathbb{C}^{M \times 1}$.
		\end{subsubsection}

@@

		Denote the baseband equivalent channels from the AP to user $k$, from the AP to the IRS, and from the IRS to user $k$ as $\boldsymbol{h}_{D,k} \in \mathbb{C}^{1 \times MN}$, $\boldsymbol{H}_I \in \mathbb{C}^{U \times MN}$, and $\boldsymbol{h}_{R,k} \in \mathbb{C}^{1 \times UN}$ respectively. At subband $n$, we collect the frequency response of both direct and reflective links from $M$ and $U$ elements to user $k$ as $\boldsymbol{h}_{D,k,n}=[h_{D,k,n,1},\dots,h_{D,k,n,M}] \in \mathbb{C}^{1 \times M}$ and $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{D,k,n,U}] \in \mathbb{C}^{1 \times U}$. Similarly, the $n$-th incident channel gain matrix from $M$ transmit antennas to $U$ reflectors is expressed as $\boldsymbol{H}_{I,n}=[\boldsymbol{h}_{I,1,n}^T,\dots,\boldsymbol{h}_{I,U,n}^T]^T \in \mathbb{C}^{U \times M}$, with $\boldsymbol{h}_{I,u,n}=[h_{I,u,n,1},\dots,h_{I,u,n,M}] \in \mathbb{C}^{1 \times M}$. Element $u$ of the IRS receives a superposed waveform through the multipath channel, then redistribute it by adjusting the reflection coefficient $r_u = \beta_u e^{j \theta_u}$, where $\beta_u \in [0,1]$ and $\theta_u \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift respectively. Each passive reflector harvests a small portion ($1 - \beta_u$) of the signal to support CSI decoding and impedance matching. Construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients of all reflectors onto the diagonal entries such that $\boldsymbol{R}_0 = \text{diag}(r_1, \dots, r_U) \in \mathbb{C}^{U \times U}$. With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{R}_0$ over $N$ subbands such that $\boldsymbol{R} = [\boldsymbol{R}_0^T,\dots,\boldsymbol{R}_0^T]^T \in \mathbb{C}^{UN \times U}$. The IRS-aided extra links can be modeled as a concatenation of the AP-IRS channel to the IRS reflection matrix and the IRS-user channel. Both the direct link and the IRS-aided link contributes to the composite channel $\boldsymbol{h}_k \in \mathbb{C}^{1 \times MN}$ as
		\begin{equation}	\label{eq:h_k}
			\boldsymbol{h}_k = \left( \boldsymbol{h}_{D,k}+\boldsymbol{h}_{R,k} \boldsymbol{R} \boldsymbol{\boldsymbol{H}_I} \right)
		\end{equation}
		On top of this, we select the $n$-th of every $N$ entries and combine them to form a subchannel as $\boldsymbol{h}_{k,n}=[h_{k,n,m},\dots,h_{k,n,M}] \in \mathbb{C}^{1 \times M}$ to describe the frequency response at subband $n$ for user $k$, where $h_{k,n,m}=h_{D,k,n,m}+\boldsymbol{h}_{R,k,n}\boldsymbol{R}_0\boldsymbol{H}_{I,n}$.
	\end{subsection}

	\begin{subsection}	{Received Signal}
		In the signal received by user $k$, the component from transmit antenna $m$ captures the contribution of information and power waveforms through both direct and reflective links as
		\begin{equation}	\label{eq:y_{m,k}(t)}
			y_{m,k}(t)=\Re\left\{\sum_{n=1}^N{(w_{I,n,m}\tilde{x}_{I,n}(t)+w_{P,n,m})h_{k,n,m}e^{j2{\pi}{f_n}t}}\right\}
		\end{equation}
		Therefore, the RF input signal to the antenna of user $k$ writes as
		\begin{equation}	\label{eq:y_k(t)}
			\begin{split}
				y_k(t)
				&=\Re\left\{\sum_{m=1}^M{y_{m,k}(t)}\right\}	\\
				&=\Re\left\{\sum_{m=1}^M{\sum_{n=1}^N{(w_{I,n,m}\tilde{x}_{I,n}(t)+w_{P,n,m})h_{k,n,m}e^{j2{\pi}{f_n}t}}}\right\}	\\
				&=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}(\boldsymbol{w}_{P,n}+\boldsymbol{w}_{I,n}\tilde{x}_n)e^{j2{\pi}{f_n}t}}\right\}
			\end{split}
		\end{equation}
		% \begin{equation}	\label{eq:y_{m,k}(t)}
		% 	\begin{split}
		% 		y_{m,k}(t)
		% 		&= \Re \left\{ \sum_{n=1}^{N} \sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} x_{n,m}(t-\tau_{l_{D,k}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{D,k}})+\varsigma_{l_{D,k},n,m,k}\right) } \right\}	\\
		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{l_{R,k}=1}^{L_{R,k}} \sum_{u=1}^{U} \alpha_{l_{R,k}} r_u \alpha_{l_{I,u}} x_{n,m}(t-\tau_{l_{R,k}}-\tau_{l_{I,u}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{R,k}}-\tau_{l_{I,u}})+\varsigma_{l_{R,k},n,u,k}+\varsigma_{l_{I,u},n,m,u}\right)} \right\}	\\
		% 		&\approx \Re \left\{ \sum_{n=1}^{N} h_{D,n,m,k}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\}	\\
		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} h_{R,n,u,k}(t) r_u h_{I,n,m,u}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\}	\\
		% 		&= \Re \left\{ \sum_{n=1}^{N} {s_{P,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\}	\\
		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {s_{P,n,m}}{A_{R,n,u,k}}{\beta_u}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{R,n,u,k}+\theta_u+\bar{\psi}_{I,n,m,u} \right)} \right\}	\\
		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} {\tilde{s}_{I,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\}	\\
		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {\tilde{s}_{I,n,m}}{A_{R,n,u,k}}{\beta_u}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{R,n,u,k}+\theta_u+\bar{\psi}_{I,n,m,u} \right)} \right\}
		% 	\end{split}
		% \end{equation}
		% Therefore, the RF signal input to the antenna at user $k$ is
		% \begin{equation}	\label{eq:y_{k}(t)}
		% 	y_{k}(t) = \sum_{m=1}^{M} y_{m,k}(t)
		% \end{equation}
	\end{subsection}

	\begin{subsection}	{Information Decoder}
		In the
	\end{subsection}
\end{section}

>>>>

		\begin{subsubsection} {Unmodulated Power Waveform}
			As suggested in \cite{Clerckx2018b,Clerckx2016a}, we use deterministic multisine waveform to boost the harvested energy. It has no randomness over time and the equivalent input power symbol $\tilde{x}_{P,n}$ is a constant on subband $n$ (i.e. $\tilde{x}_{P,n} = 1$). Therefore, on the $n$-th subcarrier of the $m$-th transmit antenna, the power weight $w_{P,n,m} = s_{P,n,m} e^{j\phi_{P,n,m}}$ represents the complex-valued sinewave (i.e. $x_{P,n,m}(t) = w_{P,n,m}$) in the baseband (BB). The transmit power waveform on the antenna $m$ at time $t$ is given by
			\begin{equation}	\label{eq:x{P,m}(t)}
				\begin{split}
					x_{P,m}(t)
					&= \sum_{n=1}^{N} s_{P,n,m}(t) \cos \left( 2 \pi f_n t + \phi_{P,n,m}(t) \right)	\\
					&= \Re \left\{ \sum_{n=1}^{N} x_{P,n,m}(t) e^{j2 \pi f_n t} \right\}	\\
					&= \Re \left\{ \sum_{n=1}^{N} w_{P,n,m} e^{j2 \pi f_n t} \right\}
				\end{split}
			\end{equation}
			The corresponding power waveform vector is stacked across $M$ transmit antennas as
			\begin{equation}	\label{eq:x_P(t)}
				\boldsymbol{x}_P(t) = \Re \left\{ \sum_{n=1}^{N} \boldsymbol{w}_{P,n} e^{j2{\pi}{f_n}t} \right\}
			\end{equation}
			where $\boldsymbol{w}_{P,n}=[w_{P,n,1},\dots,w_{P,n,M}]^T \in \mathbb{C}^{M \times 1}$.
		\end{subsubsection}

@@

		Denote the baseband equivalent channels from the AP to user $k$, from the AP to the IRS, and from the IRS to user $k$ as $\boldsymbol{h}_{D,k} \in \mathbb{C}^{1 \times MN}$, $\boldsymbol{H}_I \in \mathbb{C}^{U \times MN}$, and $\boldsymbol{h}_{R,k} \in \mathbb{C}^{1 \times UN}$ respectively. At subband $n$, we collect the frequency response of both direct and reflective links from $M$ and $U$ elements to user $k$ as $\boldsymbol{h}_{D,k,n}=[h_{D,k,n,1},\dots,h_{D,k,n,M}] \in \mathbb{C}^{1 \times M}$ and $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{D,k,n,U}] \in \mathbb{C}^{1 \times U}$. Similarly, the $n$-th incident channel matrix from $M$ transmit antennas to $U$ reflectors is expressed as $\boldsymbol{H}_{I,n}=[\boldsymbol{h}_{I,1,n}^T,\dots,\boldsymbol{h}_{I,U,n}^T]^T \in \mathbb{C}^{U \times M}$, with $\boldsymbol{h}_{I,u,n}=[h_{I,u,n,1},\dots,h_{I,u,n,M}] \in \mathbb{C}^{1 \times M}$. We also define the columns of $\boldsymbol{H}_{I,n}$ as $\boldsymbol{h}_{I,n,m}=[h_{I,1,n,m},\dots,h_{I,U,n,m}]^T$ to represent the channel between antenna $m$ and IRS. Element $u$ of the IRS receives a superposed waveform through the multipath channel, then redistribute it by adjusting the reflection coefficient $\beta_u e^{j \theta_u}$, where $\beta_u \in [0,1]$ and $\theta_u \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift respectively. Each passive reflector harvests a small portion ($1 - \beta_u$) of the signal to support CSI decoding and impedance matching. Construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients of all reflectors onto the diagonal entries such that $\boldsymbol{\Theta}_0 = \text{diag}(\beta_1 e^{j \theta_1}, \dots, \beta_U e^{j \theta_U}) \in \mathbb{C}^{U \times U}$. With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{\Theta}_0$ over $N$ subbands such that $\boldsymbol{\Theta} = [\boldsymbol{\Theta}_0^T,\dots,\boldsymbol{\Theta}_0^T]^T \in \mathbb{C}^{UN \times U}$. The IRS-aided extra links can be modeled as a concatenation of the AP-IRS channel to the IRS reflection matrix and the IRS-user channel. Both the direct link and the IRS-aided link contributes to the composite channel $\boldsymbol{h}_k \in \mathbb{C}^{1 \times MN}$ as
		\begin{equation}	\label{eq:h_k}
			\boldsymbol{h}_k = \left( \boldsymbol{h}_{D,k}+\boldsymbol{h}_{R,k} \boldsymbol{\Theta} \boldsymbol{\boldsymbol{H}_I} \right)
		\end{equation}
		On top of this, we select the $n$-th from its every $N$ entries and combine them to form a subchannel $\boldsymbol{h}_{k,n} \in \mathbb{C}^{1 \times M}$ as
		\begin{equation}	\label{eq:h_{k,n}}
			\begin{split}
				\boldsymbol{h}_{k,n}
				&=\boldsymbol{h}_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{H}_{I,n}	\\
				&=[h_{k,n,1},\dots,h_{k,n,M}]
			\end{split}
		\end{equation}
		where $h_{k,n,m}=h_{D,k,n,m}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n,m}$.
	\end{subsection}

	\begin{subsection}	{Received Signal}
		In the signal received by user $k$, the component from transmit antenna $m$ captures the contribution of information and power waveforms through both direct and reflective links as
		\begin{equation}	\label{eq:y_{m,k}(t)}
			y_{m,k}(t)=\Re\left\{\sum_{n=1}^N{(w_{I,n,m}\tilde{x}_{I,n}(t)+w_{P,n,m})h_{k,n,m}e^{j2{\pi}{f_n}t}}\right\}
		\end{equation}
		Therefore, the RF input signal to the antenna of user $k$ writes as
		\begin{equation}	\label{eq:y_k(t)}
			\begin{split}
				y_k(t)
				&=\Re\left\{\sum_{m=1}^M{y_{m,k}(t)}\right\}	\\
				&=\Re\left\{\sum_{m=1}^M{\sum_{n=1}^N{(w_{I,n,m}\tilde{x}_{I,n}(t)+w_{P,n,m})h_{k,n,m}e^{j2{\pi}{f_n}t}}}\right\}	\\
				&=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}(\boldsymbol{w}_{P,n}+\boldsymbol{w}_{I,n}\tilde{x}_n)e^{j2{\pi}{f_n}t}}\right\}	\\
				&=y_{I,k}(t)+y_{P,k}(t)
			\end{split}
		\end{equation}
		% \begin{equation}	\label{eq:y_{m,k}(t)}
		% 	\begin{split}
		% 		y_{m,k}(t)
		% 		&= \Re \left\{ \sum_{n=1}^{N} \sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} x_{n,m}(t-\tau_{l_{D,k}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{D,k}})+\varsigma_{l_{D,k},n,m,k}\right) } \right\}	\\
		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{l_{R,k}=1}^{L_{R,k}} \sum_{u=1}^{U} \alpha_{l_{R,k}} r_u \alpha_{l_{I,u}} x_{n,m}(t-\tau_{l_{R,k}}-\tau_{l_{I,u}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{R,k}}-\tau_{l_{I,u}})+\varsigma_{l_{R,k},n,u,k}+\varsigma_{l_{I,u},n,m,u}\right)} \right\}	\\
		% 		&\approx \Re \left\{ \sum_{n=1}^{N} h_{D,n,m,k}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\}	\\
		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} h_{R,n,u,k}(t) r_u h_{I,n,m,u}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\}	\\
		% 		&= \Re \left\{ \sum_{n=1}^{N} {s_{P,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\}	\\
		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {s_{P,n,m}}{A_{R,n,u,k}}{\beta_u}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{R,n,u,k}+\theta_u+\bar{\psi}_{I,n,m,u} \right)} \right\}	\\
		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} {\tilde{s}_{I,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\}	\\
		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {\tilde{s}_{I,n,m}}{A_{R,n,u,k}}{\beta_u}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{R,n,u,k}+\theta_u+\bar{\psi}_{I,n,m,u} \right)} \right\}
		% 	\end{split}
		% \end{equation}
		% Therefore, the RF signal input to the antenna at user $k$ is
		% \begin{equation}	\label{eq:y_{k}(t)}
		% 	y_{k}(t) = \sum_{m=1}^{M} y_{m,k}(t)
		% \end{equation}
	\end{subsection}

	\begin{subsection}	{Information Decoder}
		One major benefit of using proposed waveform is that as a translation, the deterministic power term $y_{P,k}(t)$ bears no information and creates no interference to the modulated information term $y_{I,k}(t)$. Therefore, the achievable rate of user $k$ is expressed as
		\begin{equation}	\label{eq:I_k}
			\begin{split}
				I_k(\boldsymbol{w}_I,\boldsymbol{\Theta},\rho)
				&=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert\boldsymbol{h}_{k,n}\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)}	\\
				&=?
			\end{split}
		\end{equation}
		where $\sigma_n^2$ is the sum variance of the Gaussian noise at the RF-band and those introduced during the RF-to-BB conversion on subband $n$. A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:I_k} is always achievable with or without waveform cancellation, by subtracting the deterministic power component or constructing a translated codebook.
	\end{subsection}

	\begin{subsection}	{Energy Harvester}
		Although the power term $y_{P,k}(t)$ have no impact on communication, both $y_{I,k}(t)$ and $y_{P,k}(t)$ contribute to energy delivery in different manner. Consider the nonlinear diode model based on the Taylor expansion of small signal model that highlights the dependency between the harvester output DC current and the received waveform \cite{Clerckx2018b,Clerckx2016a}
		\begin{equation}	\label{eq:i_k}
			i_{\text{out},k}\approx\sum_{i=0}^{\infty}{k_i'}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y(t)^i\right\}}
		\end{equation}
		where $k_i'$ depends on $i_{\text{out},k}$ and diode characteristics, $R_{\text{ant}}$ is the impedance of receive antenna. With the assumption of evenly spaced frequencies, $\mathcal{E}\left\{y(t)^i\right\}=0$ for odd $i$ which has no contribution to DC components. \cite{Clerckx2016a} also demonstrated that to maximize $i_{\text{out},k}$, it suffices to maximize the monotonic function truncated to the $n_0$ order
		\begin{equation}	\label{eq:z_{DC,k}}
			\begin{split}
				z_{DC,k}
				&=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y(t)^i\right\}}	\\
				&=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_P(t)^i\right\}}	\\
				&+\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_I(t)^i\right\}\right\}}
			\end{split}
		\end{equation}
		where $k_i=i_s/i!(nv_t)^i$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage.

	\end{subsection}
\end{section}
